### 2017-04-03 paper/evaluation.tex
show RQ# with question

\begin{itemize}
    \item \textbf{\RQA}
\end{itemize}
%\Jbc{The following steps may change $\rightarrow$}

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-long.pdf}
      \caption{\label{fig:longtcost}Long group.}
    \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-medium.pdf}
      \caption{\label{fig:medtcost}Medium group.}
    \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=.75\textwidth]{plots/boxplots-testcases.pdf}
        \caption{\label{fig:medtcost}Distribution of test cases.}
    \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=.68\textwidth]{plots/scatter-testcost.pdf}
        \caption{\label{fig:scattercost}\Fix{maybe the coordinates should be flipped}}
     \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.5\textwidth}
      \centering
      \begin{tabular}{rrrr}
        \toprule
        & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
        \midrule    
        Long   &  7 & 15 & 12 \\
        Medium & 22 & 19 & 7 \\
        \bottomrule
      \end{tabular}
      \caption{\label{fig:sd}Standard deviantion of test cases}
    \end{subfigure}%
    \caption{\label{fig:time-distributions}Distribution of test case
    execution cost per project.}%
\end{figure}

@@

To understand why developers prefer not use parallel test execution,
we considered the \numNonParallel{} subjects that do not use any
parallel mode from Section~\ref{sec:rqC-1} (\ie{}, \medg{} and
\longg{}
projects that does not run in parallel by default) and elaborated a
quick survey to extent the comprehension about why developers do not
use parallel configuration. \Luis{describe how we created the survey}.
We first retrieve the last 20 commits from the project repository and
got the developers e-mails. In total, we sent \emailsSent{} e-mails to
different developers that recently contributed to the project.
There were \emailsAnswered{} replies, and \emailsTrueAnswers{} of
those were answering the survey.

@@

\Comment{
\begin{enumerate}
	\item How long does it take for test to run in your
		environment?
	\item Can you briefly define your setup?
	\item Do you confirm that your project does not run in
		parallel?
	\item Select a reason for not using paralellization:
		\begin{enumarate}
			\item I did not know it was possible;
			\item I was concerned with concurrency issues;
			\item I use a continuous integration server;
			\item Some other reason.
		\end{enumerate}
\end{enumerate}
}
\begin{center}
\fbox{
  \begin{minipage}{8cm}
      \textit{Answering \numRQE{}:~\emph{\Luis{summarize
	  findings...}}}
  \end{minipage}
}
\end{center}

\Luis{these values need macro $\rightarrow$}
From the valid replies, we noticed that \Fix{55.2\%
(16/\emailsTrueAnswers{})} of developers use an external continuous
integration server to run tests, \Fix{27.6\% (8/\emailsTrueAnswers{})} run tests in the
development machine, \Fix{13.8\% (4/\emailsTrueAnswers{})} did
not specified the environment.

>>>>

\begin{itemize}
    \item \numRQA{}. \textbf{\RQA}
\end{itemize}
%\Jbc{The following steps may change $\rightarrow$}

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-long.pdf}
      \caption{\label{fig:longtcost}Long group.}
    \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-medium.pdf}
      \caption{\label{fig:medtcost}Medium group.}
    \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.15\textwidth}
      \centering
      \includegraphics[width=.85\textwidth]{plots/boxplots-testcases.pdf}
        \caption{\label{fig:medtcost}Distribution of test cases.}
    \end{subfigure}~
    \begin{subfigure}{0.3\textwidth}
      \centering
      \includegraphics[width=.95\textwidth]{plots/scatter-testcost.pdf}
        \caption{\label{fig:scattercost}\Fix{legend}}
     \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.5\textwidth}
      \centering
      \begin{tabular}{rrrr}
        \toprule
        & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
        \midrule    
        Long   &  7 & 15 & 12 \\
        Medium & 22 & 19 & 7 \\
        \bottomrule
      \end{tabular}
      \caption{\label{fig:sd}Standard deviantion of test cases}
    \end{subfigure}%
    \caption{\label{fig:time-distributions}Distribution of test case
    execution cost per project.}%
\end{figure}

@@

To understand why developers prefer not use parallel test execution,
we considered the \numNonParallel{} subjects that do not use any
parallel mode from Section~\ref{sec:rqC-1} and elaborated a
quick survey to extent the comprehension about why developers do not
use parallel configuration. \Luis{describe how we created the survey}.
We first retrieve the last 20 commits from the project repository and
got the developers e-mails. In total, we sent an e-mail to
\emailsSent{} developers that recently contributed to the
\numNonParallel{} projects.
There were \emailsAnswered{} replies, and \emailsTrueAnswers{} of
those were answering the survey.

@@

\Comment{
\begin{enumerate}
	\item How long does it take for test to run in your
		environment?
	\item Can you briefly define your setup?
	\item Do you confirm that your project does not run in
		parallel?
	\item Select a reason for not using paralellization:
		\begin{enumarate}
			\item I did not know it was possible;
			\item I was concerned with concurrency issues;
			\item I use a continuous integration server;
			\item Some other reason.
		\end{enumerate}
\end{enumerate}
}

From the valid replies, we confirmed that the projects we sent the
e-mails takes more than 1 minute to run tests and \emailsSeq{}
confirmed that those projects do not use parallel testing using Maven
Surefire. The other projects that we do not confirm, need and extra
parameter to execute in parallel mode \Luis{make sure that they are
inside the static analysis sheets made before}.

We noticed that \pctEmailsCI{} of developers use an continuous integration 
server to run tests, \pctEmailsLocal{} run tests in the
development machine, \pctEmailsDidNotSpecify{} did not specified their
testing setup.
We also noticed that one project has testing enabled without parallel 
configuration, however, the maintainers never run the test. 
Considering developers did not know about the existence of the
parallelism configuration \pctEmailsDoNotKnow{} of the replies
confirmed that. Three of the developers also confirmed that they use
another method of parallelization with distributed build machines.

\begin{center}
\fbox{
	\begin{minipage}{8cm}
		\textit{Answering \numRQE{}:~\emph{\Luis{summarize
		findings...}}}
	\end{minipage}
}
\end{center}
